\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Conclusion

\section{Statistics}
\label{Statistics}
In this section we will discuss the statistical data that have been gathered from our logfiles. 
The logged connection attempts have been processed to group them by the IP address' originating country through the use of WHOIS directory service information.
It is worthwhile noting that a significant number of connecting hosts could not be referenced to RWHOIS information.
Also note that these graphs display all logged connection attempts rather than successful connections, giving us a general view of which ports attract attention.

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Attacks} we can conclude that our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.

Concluding:

>>>>

\section{Statistics}
\label{Statistics}
In this section we will discuss the statistical data that have been gathered from our logfiles. 
The logged connection attempts have been processed to group them by the IP address' originating country through the use of WHOIS directory service information.
It is worthwhile noting that a significant number of connecting hosts could not be referenced to RWHOIS information.
In these cases we have attempted to resolve the missing information by making use of reverse DNS queries and grouping by associated top level domain.
Also note that these graphs display all logged connection attempts rather than successful connections, giving us a general view of which ports attract attention.

@@

\section{Conclusion}
\label{Conclusion}
The Setup we used for this honeypot seems to be sufficient. In both phases of the research we did not lose control over our honeypot, which was our main worry. We also decided not to advertise, which gave our honeypot less traffic, but a more realistic outcome.

From the Section Attacks we can conclude that our honeypot was not as popular as we had hoped it would be. We blame this on not advertising our IP. The numbers of attacks on us were therefore not high and neither was the depth of the attacks.

Only three real scans took place, as reported in the Section Connections between attacks. Unfortuntaly we did not make our honeypot interesting enough for them to return and actually break in.

Our chose for swiching from a Low Interaction to a High Interaction honeypot seems like a good tactic, but due to downtime and bugged software, we did not have enough time.

Concluding: we did see some people checking us out, but noone actually broke in. For further research we suggest using the same setup, but having the server online for a much longer time.
